results notes

### 2022-09-02 RR_manuscript/results_notes.Rmd
add sample descriptives, include in text

library(brms)
library(faux)
library(dplyr)
library(ggplot2)
library(tidybayes)
library(here)

@@

# Get DF of all members with leader names
#
# NOTE: This can be simplified using 03_analyses_coding.Rmd
# I'll come back to this later and rewrite
#
team_leaders <- readr::read_csv(
  here::here("data", "questionnaires", "msa_intake_form.csv")) %>% 
  select(ResponseId, Q6) %>% # Questions asking for team leader
  filter(!(row_number() %in% c(1, 2))) %>% 
  mutate(leader = Q6, 
    leader = case_when(
    Q6 %in% c("Ali A-Hoorie", "Ali Al-Hoorie", "Ali H. Al-Hoorie") ~ "Ali Al-Hoorie", 
    Q6 %in% c("Alicea Megan Brown", "Alicia Brown") ~ "Alicia Brown", 
    Q6 %in% c("Dr Rory Turnbull", "Rory Turnbull") ~ "Rory Turnbull", 
    Q6 %in% c("Dr. Reenu Punnoose", "Reenu Punnoose") ~ "Reenu Punnoose", 
    Q6 %in% c("Dušan Nickolić", "Dušan Nikolić", "Dusan Nikolic", "Dusan Nikolic (dusan.nikolic1@ucalgary.ca)") ~ "Dusan Nikolic", 
    Q6 %in% c("Michael Gradoville (Arizona State Univ.)", "Michael Gradoville") ~ "Michael Gradoville", 
    Q6 %in% c("Nicole Rodriquez", "Nicole Rodriguez") ~ "Nicole Rodriguez", 
    Q6 %in% c("Scott James Perru", "Scott Perry") ~ "Scott James Perru", 
    Q6 %in% c("Tiphaine Caudrelier", "Tiphaine Cordelier") ~ "Tiphaine Caudrelier", 
    Q6 %in% c("University of Birmingham team under the team coordinator Zlatomira IIchovska", "Zlatomira IIchovska", "Zlatomira Ilchovska") ~ "Zlatomira Ilchovska", 
    Q6 %in% c("Vincent Hughes", "Vince Hughes") ~ "Vincent Hughes", 
    TRUE ~ leader
  )) %>% 
  select(ResponseId, leader)

# Team descriptives
#  - number of teams (initially)
#  - Avg size of each team
team_desc <- team_leaders %>% 
  group_by(leader) %>% 
  mutate(member_num = seq_along(ResponseId)) %>% 
  group_by(leader) %>% 
  mutate(n_members = max(member_num)) %>% 
  distinct(leader, n_members) %>% 
  ungroup() %>% 
  summarize(n_teams = nrow(.), 
            mean_size = mean(n_members), 
            sd_size = sd(n_members), 
            median_size = median(n_members))

# Need to join team leaders with msa_models$team to get the number of members on 
# each team (unless this data already lives somewhere else) 
# We could use : 
# https://docs.google.com/spreadsheets/d/1w39rU7O5ijzPmCpClVt5LEDIhzaLBDNrwfdMJUP86q8/edit#gid=0 
# But I'm thinking we need to make anonymous the team leader name info (offline) 
# for any of this to be a permanent solution.

@@

`r team_desc$n_teams %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate. 
`r (team_desc$n_teams - no_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the proposed teams dropped out of the project during the analysis phase^[ADD REASONS]. 
The remaining `r no_teams` teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).

<!-- TR: not just 30 right? Please add the accurate info here -->
<!-- 
JVC: I pulled the initial total from the uptake doc (see line 58-n) 
I think this is the most accurate count, by Stef might have another way
-->

Of the submitted teams, teams consisted of an average of xx analysts (sd = xx) <!-- TR: Where is this info? -->. Analysts had on average `r round(phd_mean[[1]],1)` years (sd = `r round(phd_mean[[2]],1)`) post PhD experience, ranging from `r round(phd_mean[[3]],1)` years, i.e. PhD students (or younger) to `r round(phd_mean[[4]],1)` years.

>>>>

library(brms)
library(faux)
library(dplyr)
library(ggplot2)
library(tidybayes)
library(here)
library(googlesheets4)

@@

# Helper function to print table data easier
split_to_list <- function(.data, ...) {
  dots <- rlang::enquos(...)
  for (var in seq_along(dots)) {
    var_name <- rlang::as_name(dots[[var]])
    .data <- purrr::map_depth(
      .x = .data,
      .depth = var - 1,
      .f = function(xs) split(xs, xs[var_name])
    )
  }
  .data
}

team_sheet <- "https://docs.google.com/spreadsheets/d/1w39rU7O5ijzPmCpClVt5LEDIhzaLBDNrwfdMJUP86q8/edit?usp=sharing"
teams <- read_sheet(team_sheet)

# Get DF of all members with leader names
team_leaders <- readr::read_csv(
  here::here("data", "questionnaires", "msa_intake_form.csv")) %>% 
  select(ResponseId, Q6) %>% # Questions asking for team leader
  filter(!(row_number() %in% c(1, 2))) %>% 
  mutate(leader = Q6, 
         leader = case_when(
           Q6 %in% c("Ali A-Hoorie", "Ali Al-Hoorie", "Ali H. Al-Hoorie") ~ "Ali H. Al-Hoorie", 
           Q6 %in% c("Alicea Megan Brown", "Alicia Brown") ~ "Alicia M Brown", 
           Q6 %in% c("Dr Rory Turnbull", "Rory Turnbull") ~ "Rory Turnbull", 
           Q6 %in% c("Dr. Reenu Punnoose", "Reenu Punnoose") ~ "Reenu Punnoose", 
           Q6 %in% c("Dušan Nickolić", "Dušan Nikolić", "Dusan Nikolic", "Dusan Nikolic (dusan.nikolic1@ucalgary.ca)") ~ "Dušan Nikolić", 
           Q6 %in% c("Michael Gradoville (Arizona State Univ.)", "Michael Gradoville") ~ "Michael Gradoville", 
           Q6 %in% c("Nicole Rodriquez", "Nicole Rodriguez") ~ "Nicole Rodriguez", 
           Q6 %in% c("Scott James Perru", "Scott Perry") ~ "Scott James Perry", 
           Q6 %in% c("Tiphaine Caudrelier", "Tiphaine Cordelier") ~ "Tiphaine Caudrelier", 
           Q6 %in% c("University of Birmingham team under the team coordinator Zlatomira IIchovska", "Zlatomira IIchovska", "Zlatomira Ilchovska") ~ "Zlatomira Ilchovska", 
           Q6 %in% c("Vincent Hughes", "Vince Hughes") ~ "Vince Hughes", 
           Q6 == "Joey Stanley" ~ "Joseph A. Stanley",
           TRUE ~ leader
         )) %>% 
  select(ResponseId, leader)

# Teams on OSF
teams_on_osf <- teams %>% 
  filter(added_on_osf == "yes") %>% 
  pull(coordinator)

# Teams with submitted analyses
teams_used_in_analysis <- teams %>% 
  filter(animal %in% msa_models$animal) %>% 
  pull(coordinator)

# Team descriptives
#  - number of teams (initially)
#  - Avg size of each team
team_desc_df <- bind_rows(
  team_leaders %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members)) %>% 
    mutate(stage = "Initial"), 
  team_leaders %>% 
    filter(leader %in% teams_on_osf) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members)) %>% 
    mutate(stage = "Submitted"), 
  team_leaders %>% 
    filter(leader %in% teams_used_in_analysis) %>% 
    group_by(leader) %>% 
    mutate(member_num = seq_along(ResponseId)) %>% 
    group_by(leader) %>% 
    mutate(n_members = max(member_num)) %>% 
    distinct(leader, n_members) %>% 
    ungroup() %>% 
    summarize(n_teams = nrow(.), 
              mean_size = mean(n_members), 
              sd_size = sd(n_members), 
              median_size = median(n_members)) %>% 
    mutate(stage = "Final")
  ) %>% 
  mutate_if(is.numeric, round, digits = 2)

team_desc_list <- team_desc_df %>% 
  tidyr::pivot_longer(cols = n_teams:median_size, names_to = "metric", values_to = "val") %>% 
  split_to_list(stage, metric)

# Example usage
# team_desc_list$Initial$n_teams$val

@@

`r team_desc_list$Initial$n_teams$val %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate. 
`r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the proposed teams dropped out of the project during the analysis phase^[ADD REASONS]. 
The remaining `r team_desc_list$Final$n_teams$val` teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).

Of the submitted teams, teams consisted of an average of `r team_desc_list$Final$mean_size$val` analysts (sd = `r team_desc_list$Final$sd_size$val`). 
Analysts had on average `r round(phd_mean[[1]],1)` years (sd = `r round(phd_mean[[2]],1)`) post PhD experience, ranging from `r round(phd_mean[[3]],1)` years, i.e. PhD students (or younger) to `r round(phd_mean[[4]],1)` years.

```{r}
#| label: team-descriptives-table
#| echo: false
#| eval: false
team_desc_df %>% 
  mutate(Mean = glue::glue("{mean_size} ({sd_size})")) %>% 
  select(Stage = stage, n = n_teams, Mean, Median = median_size) %>% 
  knitr::kable(align = c("l", "r", "r", "r"), 
               caption = "Caption test", 
               label = "team-descriptives-table")
```
